---
title: "Asteroid Impact"
author: "Bamini Balaji"
date: "July 30, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, include=FALSE, comment=FALSE, warning=FALSE}
impacts <- read.csv("C:/Users/bamini/Documents/Coursera/Developing_Data_Products/Week3/impacts.csv", header = TRUE, fileEncoding="UTF-8-BOM")
impacts$Object.Name <- as.character(impacts$Object.Name)
orbits <- read.csv("C:/Users/bamini/Documents/Coursera/Developing_Data_Products/Week3/orbits.csv", header = TRUE, fileEncoding="UTF-8-BOM")
orbits$Object.Name <- as.character(orbits$Object.Name)
orbits$Object.Name <- gsub("\\(", "", orbits$Object.Name)
orbits$Object.Name <- gsub("\\)", "", orbits$Object.Name)
asteroids <- merge(impacts, orbits, by = "Object.Name", all.x = TRUE, all.y = FALSE)
asteroids <- droplevels(asteroids)
library(plotly)
```

## Asteroid Impact

- This is an analysis using data that was collected by NASA's Near Earth Object Program. 
- The data consists of an asteroid catalog for possibilities of future impact with Earth over the next 100 years. 
- The **Palermo Scale** is used by astronomers to rate the potential hazard of impact.
- Let's look at possible factors that affect the Palermo Scale


***
```{r echo=FALSE}
plot_ly(asteroids, x = ~log(Cumulative.Impact.Probability), y = ~Cumulative.Palermo.Scale, size = ~Asteroid.Diameter..km., color = ~Asteroid.Velocity, mode = "markers", type = "scatter", text = ~paste("Asteroid: ", Object.Name))
```
Paleromo Scale versus Impact Probability (x-axis), Asteroid Velocity (color gradient) and Asteroid diameter (marker size) 
